sem

### 2022-12-09 scripts/workshop/sem.Rmd
add significant relationship from dsep test

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- gam(log10(cc) ~ s(MeanWaterTempPredC), family = gaussian, data = comm_data)
size_temp <- gam(log10(size) ~ s(MeanWaterTempPredC), family = gaussian, data = comm_data)
prev_cc <- glm(Prevalence ~ log10(cc) + log10(size), data = comm_data)

>>>>

How to model nonlinear effect of temperature?
- hump-shaped relationship may be expected with temperature

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- glm(log10(cc) ~ (MeanWaterTempPredC), data = comm_data)
size_temp <- glm(log10(size) ~ (MeanWaterTempPredC) + log10(cc), data = comm_data)
prev_cc <- glm(Prevalence ~ log10(cc) + log10(size), data = comm_data)
